\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Dungeon Dudes Write-Up}
\author{Jerimiah Katen}
\date{February 2021}

\begin{document}

\maketitle

\section{Project Summary}

Dungeon Dudes is a light text based dungeon crawler game. The game has a player move through areas with random monsters in them. The player has to fight the monsters using dice based rolls to calculate whether or not an attack hits or misses. Once the player has defeated a monster, said monster has a chance to drop loot, which the player can choose to pick up. When all of the monsters a room are defeated the player can move to the next room. After an arbitrary number of rooms and monsters (minimum of 5 for both), the player will be declared victorious and the game will end.

\section{Challenges}

\\[.5cm]
I probably made the project way harder than it needed to be. After briefly reading the requirements, I had an idea of how I wanted to do things. But, I realized that I was getting ahead of myself after more thoroughly reading the requirements. I thought I was going to have to backpedal a bit to make everything work, but I chose to give myself a huge headache and just meet the requirements with what I had.
\\[.5cm]
Some of the requirements were unclear and I just went with it. Then I got clarification and had to either re-write a bit of my code or just make it wok.


\section{Successes}
I enjoyed this project. It is a nice chance of pace from the C projects.

\section{Lessons Learned}
I really like object oriented programming, but I'm not sure if I actually know what I'm doing yet.

\end{document}
